### 2017-06-20 Docs/Thesis/docs/appendix/appendixB.tex
modifications

>>>>

\begin{table}[ht!]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{@{}ll@{}}
\toprule
Traffic Generator       & Repository                                                                                                                                                                                                                \\ \midrule
D-ITG                   & \href{http://traffic.comics.unina.it/software/ITG/}{http://traffic.comics.unina.it/software/ITG/}                                                                                                                         \\
Ostinato                & \href{http://ostinato.org/}{http://ostinato.org/}                                                                                                                                                                         \\
Seagull                 & \href{http://gull.sourceforge.net/}{http://gull.sourceforge.net/}                                                                                                                                                         \\
BRUTE                   & \href{http://wwwtlc.iet.unipi.it/software/brute/ }{http://wwwtlc.iet.unipi.it/software/brute/ }                                                                                                                           \\
PackETH                 & \href{http://packeth.sourceforge.net/packeth/Home.html}{http://packeth.sourceforge.net/packeth/Home.html}                                                                                                                 \\
Iperf                   & \href{https://iperf.fr/}{https://iperf.fr/}                                                                                                                                                                               \\
NetPerf                 & \href{http://www.netperf.org/netperf/}{http://www.netperf.org/netperf/}                                                                                                                                                   \\
sourcesOnOff            & \href{http://www.recherche.enac.fr/~avaret/sourcesonoff}{http://www.recherche.enac.fr/~avaret/sourcesonoff}                                                                                                               \\
TG                      & \href{http://www.postel.org/tg/}{http://www.postel.org/tg/}                                                                                                                                                               \\
MGEN*                   & \href{http://www.nrl.navy.mil/itd/ncs/products/mgen }{http://www.nrl.navy.mil/itd/ncs/products/mgen }                                                                                                                     \\
KUTE                    & \href{http://caia.swin.edu.au/genius/tools/kute/}{http://caia.swin.edu.au/genius/tools/kute/}                                                                                                                             \\
RUDE \& CRUDE            & \href{http://rude.sourceforge.net/}{ http://rude.sourceforge.net/}                                                                                                                                                        \\
Pktgen                  & \href{http://www.linuxfoundation.org/collaborate/workgroups/networking/pktgen}{http://www.linuxfoundation.org/collaborate/workgroups/networking/pktgen}                                                                   \\
NetSpec                 & \href{http://www.ittc.ku.edu/netspec/}{http://www.ittc.ku.edu/netspec/}                                                                                                                                                   \\
Nping                   & \href{https://nmap.org/nping/ }{https://nmap.org/nping/}                                                                                                                                                                  \\
TCPreplay               & \href{http://tcpreplay.appneta.com/}{http://tcpreplay.appneta.com/}                                                                                                                                                       \\
TCPivo                  & \href{http://www.thefengs.com/wuchang/work/tcpivo/}{http://www.thefengs.com/wuchang/work/tcpivo/}                                                                                                                         \\
NetFPGA PacketGenerator & \href{https://github.com/NetFPGA/netfpga/wiki/PacketGenerator}{https://github.com/NetFPGA/netfpga/wiki/PacketGenerator}                                                                                                   \\
NetFPGA Caliper         & \href{https://github.com/NetFPGA/netfpga/wiki/PreciseTrafGen}{https://github.com/NetFPGA/netfpga/wiki/PreciseTrafGen}                                                                                                     \\
NetFPGA OSNT            & \href{https://github.com/NetFPGA/OSNT-Public/wiki/OSNT-Traffic-Generator}{https://github.com/NetFPGA/OSNT-Public/wiki/OSNT-Traffic-Generator}                                                                             \\
DPDK Pktgen             & \href{http://pktgen.readthedocs.io/en/latest/getting_started.html}{http://pktgen.readthedocs.io/en/latest/getting\_started.html}                                                                                          \\
MoonGen                 & \href{https://github.com/emmericp/MoonGen}{https://github.com/emmericp/MoonGen}                                                                                                                                           \\
gen\_send/gen\_recv       & \href{http://www.citi.umich.edu/projects/qbone/generator.html}{http://www.citi.umich.edu/projects/qbone/generator.html}                                                                                                   \\
mxtraf                  & \href{http://mxtraf.sourceforge.net/}{http://mxtraf.sourceforge.net/}                                                                                                                                                     \\
JTG                     & \begin{tabular}[c]{@{}l@{}}\href{https://sourceforge.net/projects/iperf/files/}{https://sourceforge.net/projects/iperf/files/}\\ \href{https://github.com/AgilData/jperf}{https://github.com/AgilData/jperf}\end{tabular} \\
GenSyn                  & \href{http://www.item.ntnu.no/people/personalpages/fac/poulh/gensyn}{http://www.item.ntnu.no/people/personalpages/fac/poulh/gensyn}                                                                                       \\
SURGE                   & \href{http://cs-www.bu.edu/faculty/crovella/surge_1.00a.tar.gz}{http://cs-www.bu.edu/faculty/crovella/surge\_1.00a.tar.gz}                                                                                                \\
Httperf                 & \href{https://linux.die.net/man/1/httperf}{https://linux.die.net/man/1/httperf}                                                                                                                                           \\
VoIP Traffic Generator  &                                                                                                                                                                                                                           \\
Harpoon                 & \href{http://cs.colgate.edu/~jsommers/harpoon/}{http://cs.colgate.edu/~jsommers/harpoon/}                                                                                                                                 \\
Swing                   & \href{http://cseweb.ucsd.edu/~kvishwanath/Swing/}{http://cseweb.ucsd.edu/~kvishwanath/Swing/}                                                                                                                             \\
NFPA                    &                                                                                                                                                                                                                           \\
LegoTG                  &                                                                                                                                                                                                                           \\ \bottomrule
\end{tabular}
\end{table}

### 2017-06-20 Docs/Thesis/docs/chapter4.tex
modifications

>>>>

\begin{table}[!ht]
\begin{tabular}{@{}|l|l|@{}}
\toprule
Link                                & \multirow{3}{*}{\textit{headers data}} \\ \cmidrule(r){1-1}
Network                             &                                        \\ \cmidrule(r){1-1}
Transport                           &                                        \\ \midrule
Application                         & appClassification                      \\ \midrule
\multirow{2}{*}{Inter Packet Times} & calcOnOff                              \\ \cmidrule(l){2-2} 
                                    & stochasticFitting                      \\ \midrule
Packet Size                         & stochasticFitting                      \\ \bottomrule
\end{tabular}
\end{table}
